---
title: "hw01_gapminder"
author: "Xinzhe Dong"
date: "September 16, 2017"
output: 
  github_document
---

##Get an overview of the gapminder dataframe
####1. Get the Gapminder data
```{r}
library(gapminder)
str(gapminder)
```

####2. Print gapminder to screen
```{r}
library(tidyverse)
gapminder
```

####3. A statistical overview of gapminder data
```{r}
summary(gapminder)
```

####4. Understand the basic extent of the data frame: number of rows and columns.
```{r}
ncol(gapminder)
nrow(gapminder)
```

####5. Some basic plots
```{r}
plot(lifeExp ~ year, gapminder)
plot(lifeExp ~ gdpPercap, gapminder)
plot(lifeExp ~ log(gdpPercap), gapminder)
plot(lifeExp ~ pop, gapminder)

```

##Look at the variables inside a data frame
####1. Life expectancy is a numeric variable.
```{r}
head(gapminder$lifeExp)
summary(gapminder$lifeExp)
hist(gapminder$lifeExp)
```

####2. The year variable is an integer variable.
```{r}
summary(gapminder$year)
table(gapminder$year)

```

####3. The variable continent is a categorical variable, which is stored as a factor in R.
```{r}
class(gapminder$continent)
summary(gapminder$continent)
levels(gapminder$continent)
barplot(table(gapminder$continent))

```

####4. The variable country is also a categorical variable. 
```{r}
class(gapminder$country)
nlevels(gapminder$country)
```

####5. The pop variable is an integer variable.
```{r}
summary(gapminder$pop)
```

####6. gdpPercap is a numeric variable.
```{r}
summary(gapminder$gdpPercap)
hist(gapminder$gdpPercap)
```
